---
title: "README"
author: "David Hugh-Jones"
date: "8 September 2015"
output: html_document
---

```{r, echo = FALSE, eval = FALSE}
# to create README.md
library(rmarkdown)
render("README.Rmd", md_document(fig_width = 4, fig_height = 3))
```
# ffplot

`ffplot` is the fast, friendly plotting command for R. 

`ffplot` is a simple and intuitive frontend around `ggplot2`. The goal is that you can use it without thinking or 
looking up documentation.

Status: totally alpha! Download and enjoy. 

## Install

```{r, eval = FALSE}
library(devtools)
install_github("hughjonesd/ffplot")
```


## Examples

```{r}
library(ffplot)
library(ggplot2)
data(diamonds)
d30 <- diamonds[1:30,]
head(d30)
```


Simple scatterplots: 

```{r}
ffplot(price ~ carat, d30)
```

Plot numeric data by categories: 

```{r}
ffplot(price ~ color, d30)
```

Barplot of categorical data:

```{r}
ffplot(cut ~ color, d30)
```

Density plot, if right hand side is numeric:

```{r}
ffplot(cut ~ depth, d30)
```


Plot a function of your data:

```{r}
ffplot(range(price) ~ color, d30)
```

`ffplot` tries to guess what you want:

```{r}
ffplot(ci(price, 0.95) ~ color, d30)
```


Plot data with summary statistics:

```{r}
ffplot(price + mean(price) ~ color, d30)
```

Use any functions:

```{r}
ffplot(mean(price) + ci(price, .99) ~ color, d30)
```

Barplot with confidence intervals:

```{r}
ffplot(mean(price) + ci(price, .99) ~ color, d30, geom = c("bar", "errorbar"), col = "orange")
```

Add `ggplot2` options:

```{r}
ffplot(cut ~ color, diamonds) + scale_fill_grey()
```

Plus, bonus `fftable` function:

```{r}
fftable(range(carat) ~ color, diamonds)
```

## TODO

* Auto-smoothing for continuous x variables.
* Better ability to override defaults; probably something like:
```{r, eval = FALSE}
ffplot(violin(carat) + point(mean(carat)) ~ color, diamonds)
```
* More geoms
* Confidence interval function for binomial data
* Facetting
