---
title: "ffplot: a fast, friendly plotting command for R"
author: "David Hugh-Jones"
date: "11 September 2015"
output: html_document
---

```{r, echo = FALSE, eval = FALSE}
# to create README.md
library(rmarkdown)
render("README.Rmd", md_document(fig_width = 4.5, fig_height = 3))
```

`ffplot` is a simple and intuitive plotting command. The goal is that you can use it without thinking or looking up
documentation. 

Status: totally alpha! Download and enjoy. 

## Install

```{r, eval = FALSE}
library(devtools)
install_github("hughjonesd/ffplot")
```


## Examples

The basic form of every `ffplot` command is:

```{r, eval = FALSE}
ffplot(y_variables ~ x_variable, data)
```

The data is split up by unique values of x, and y variables are calculated. We'll demonstrate using the `diamonds`
data from ggplot2.

```{r}
library(ffplot)
data(diamonds, package = "ggplot2")
d30 <- diamonds[1:30,]
head(d30)
```

Here's a simple scatterplot. 

```{r}
ffplot(price ~ carat, diamonds)
```

If x and y are not numeric, we get a barplot by default. We'll see how to change this later.

```{r}
ffplot(cut ~ color, diamonds) 
```

If y is not numeric but x is, you get a density plot:

```{r}
ffplot(cut ~ depth, diamonds, position = "fill") 
```


y variables can also be functions of your data. `ffplot` tries to choose an appropriate way to display results:

```{r}
ffplot(range(price) ~ color, d30) 
```

Of course x variables can be functions too:
```{r}
ffplot(price ~ cut(carat, 5), diamonds) 
```

If you want to use a different plot type, just put it on the left:

```{r}
ffplot(boxplot(price) ~ cut, diamonds)
```

You combine plots by adding terms. Here's a smooth line:

```{r}
ffplot(price + smooth(price) ~ carat, diamonds) 
```

Here we draw means and confidence intervals. `ffplot` guesses that you want error bars for the built-in `ci` function:

```{r}
ffplot(mean(price) + ci(price, 0.95) ~ cut, diamonds) 
```

You can add `ggplot` options to the plot:

```{r}
ffplot(price ~ carat, d30, shape = 3, color = "darkgreen")
```

Or you can add options for each y variable. If so, you'll need to specify the `geom` explicitly:
```{r}
ffplot(point(price, alpha = 0.2, color = "red") + smooth(price, color = "orange", size = 2, se = TRUE) ~ carat, diamonds)
```

To create facets, just put them in the formula after a vertical bar:
```{r}
ffplot(price ~ carat | color, diamonds)
```

Two-way facets:
```{r}
x <- ffplot(smooth(mean(price)) ~ carat | color + cut, diamonds)

suppressMessages(print(x)) # annoying warning messages...
```


`ffplot` returns a `ggplot` object, so you can add functions just as with ggplot2.

```{r}
library(ggplot2)
ffplot(cut ~ color, diamonds) + scale_fill_grey()
```

It's easy to use with `dplyr` or `magrittr`:

```{r}
library(dplyr)
diamonds %>% ffplot(cut ~ color)
```


If you want to see what the underlying data looks like, there's the `fftable` function:

```{r}
fftable(range(carat) ~ color, diamonds)
```

## Cookbook

Plot proportions in a group:
```{r}
ffplot(hist(cut, position = "fill") ~ color, diamonds)
```


Barplot with confidence intervals:

```{r}
ffplot(bar(mean(price)) + ci(price, 0.99) ~ color, diamonds) 
```

Barplot of proportions with binomial confidence intervals:
```{r}
ffplot(prop(cut == "Ideal") + ci(cut == "Ideal") ~ color, diamonds)
```

Other ggplot2 `geoms` you can use:
```{r}
ffplot:::geom_names
```

## TODO

* Auto-smoothing for continuous x variables (DONE for single x)
* Better ability to override defaults (DONE)
* More geoms (DONE)
* `ci` function for binomial data (DONE)
* Facetting (DONE)
* `se` function for standard errors?
* replace auto-barplot with some kind of `props()` function?
